Selective stock enhancement undermines community stability

### 2021-12-29 rmd/manuscript.Rmd
Update manuscript.Rmd

Although captive breeding programs pay close attention to the fate of captive-bred individuals in the wild, it is rare to consider the ecosystem's capacity to support biodiversity. We anticipate that the destabilizing effect of stock enhancement is pervasive across taxa because negative density dependence is a general regulating mechanism of biodiversity. In particular, resource competition may be intensified in the Anthropocene because human influences have caused substantial loss and degradation of natural habitats. Therefore, one important implication of this study is that priorities should be given to the preservation and restoration of natural habitats with a broader focus on biodiversity. For example, recent research underscores the importance of conserving a diverse habitat portfolio that may buffer the impacts of rapid environmental changes. Without a comprehensive framework that appreciates the ecological integrity of self-sustaining communities, stock enhancement will never be effective but impairs biodiversity.

>>>>

## Implications

Although captive breeding programs pay close attention to the fate of captive-bred individuals in the wild, it is rare to consider the self-regulation process of biodiversity. The results of this study demonstrate that the ignorance of this critical process will erode the long-term persistence of the recipient community. The destabilizing effect of stock enhancement is likely to be pervasive across terrestrial and aquatic taxa because negative density dependence is a general regulating mechanism of biodiversity. We anticipate that the undesired influence of stock enhancement may be even more apparent in degraded habitats due to the compromised capacity to support biodiversity. Therefore, it is essential for us to shift our focus to the preservation and restoration efforts of natural habitats. For example, a modern conservation initiative underscores the importance of conserving a diverse habitat portfolio that may buffer the impacts of rapid environmental changes. Without a broader framework that appreciates the ecological integrity of self-sustaining communities, stock enhancement will never be effective but impairs biodiversity.
